---
title: "Bioinformatics Core Facility Rates"
output:
  html_document:
    df_print: paged
---

Introduction
============

To try to get a sense for the market for bioinformatics services I have collected hourly rate data from as many bioinformatics core facilities as I could find.  The data was collected on 3rd April 2024 and all prices are converted into UK pounds at the advertised exchange rates on the day.

```{r message=FALSE, echo=FALSE, warning=FALSE}
library(tidyverse)
theme_set(theme_bw())
```

Data
====

This is the data I collected.  Where a range of rates were advertised I took the lowest and highest prices.  These mostly represent the difference between prices for internal and external customers, but for some facilities they make a distinction based on who is doing the analysis - ie MSc researchers costs less per hour than having the facility director work on the data.

```{r message=FALSE, echo=FALSE}
read_delim("rate_data.txt") -> rate_data
rate_data %>% arrange(Organisation)
```

Visualisation
=============

```{r fig.width=6, fig.height=8, echo=FALSE}
rate_data %>%
  select(-URL) %>%
  mutate(median=apply(cbind(`Rate (low)`,`Rate (high)`),1,median)) %>%
  arrange(median) %>%
  mutate(Organisation=factor(Organisation, levels=Organisation)) -> plot_data

plot_data %>%
  ggplot(aes(x=Organisation, y=`Rate (low)`,ystart=`Rate (low)`, yend=`Rate (high)`, xstart=Organisation, xend=Organisation)) +
  geom_segment(linewidth=2, colour="darkgrey") +
  geom_point(colour="magenta3", size=3) +
  geom_point(aes(y=`Rate (high)`), colour="red2", size=3) +
  coord_flip() +
  ylab("Hourly Rate (UK Pounds)") +
  xlab(NULL) 
```

